Parkinson's disease cluster analysis

### 2016-05-08 writeup/manuscript/manuscript.tex
Pub-ready tables, more analysis of nms30

% Use times font
\usepackage{pslatex}

@@

% Tables, Figures
\usepackage{booktabs}
\usepackage{threeparttable}
\usepackage{float}
\usepackage{caption}
\setlength{\tabcolsep}{10pt}

@@

Out of the 951 patients in the study, we used listwise deletion to exclude 50 patients due to
missing measurements in the variables of interest, resulting in 901 remaining patients. All
symptoms were scaled to $z$-scores ($\mu = 0$, $\sigma = 1$) before clustering, and unscaled
afterwards. Analysis was conducted in R 3.2.4 (www.r-project.org).

@@

For each symptom in both clusterings, we used one-way ANOVA to test the equality of symptom means
across the clusters found, using Bonferroni correction for multiple testing with corrected $p <
0.05$ considered significant. Differences among pairwise clusters were tested post-hoc using
Tukey's range test.

@@

$k$-means clustering on the nine nonmotor domains and the four motor symptoms found four clusters,
available in Table~\ref{tab:nmd} with boxplots in Figure~\ref{fig:box}. Cluster means for all
symptoms were found to be statistically different, with specific pairwise differences noted in the table.

Cluster 1 ($n = 406$) patients were mildly affected in all domains.

Cluster 2 ($n = 189$) patients were severely
affected in nonmotor domains but mildly affected in motor domains (Nonmotor-Dom), cluster 3 ($n =
221$) patients were severely affected in motor domains but mildly affected in nonmotor domains
(Motor-Dom), and cluster 4 ($n = 88$) patients were severely affected in all domains. Statistics
for variables not used in the clustering were explored in Table~\ref{tab:nmd_extra}.

\begin{table*}[t]
  \centering
  \caption{Summaries of clustering on nonmotor domains. Bold indicates the highest score for that
  symptom out of the four clusters.}
  \label{tab:nmd}
  \begin{threeparttable}
  \begin{tabular}{l r r r r}
    \toprule
    Cluster & 1 & 2 & 3 & 4 \\
    $n$ & 406 (44.9\%) & 189 (20.9\%) & 221 (24.4\%) & 88 (9.7\%) \\
    \midrule
    \textbf{Nonmotor} (Domains) & & & & \\
    Cardiovascular (0--24) & 0.7 (1.6)\tnote{24} & 2.3 (2.9)\tnote{134} & 1.1 (2.0)\tnote{24} &
    \textbf{7.0} (6.0)\tnote{234} \\
    Sleep/fatigue (0--48) & 4.3 (4.8)\tnote{234} & 14.9 (8.2)\tnote{134} & 6.9 (6.3)\tnote{124}
    & \textbf{21.0} (10.0)\tnote{123} \\
    Mood/cognition (0--60) & 3.1 (4.5)\tnote{234} & 16.1 (14.0)\tnote{134} & 6.6
    (8.1)\tnote{124} & \textbf{23.4} (14.3)\tnote{123} \\
    Perception/hallucination (0--36) & 0.5 (1.7)\tnote{24} & 1.9 (3.5)\tnote{134} & 0.8
    (2.0)\tnote{24} & \textbf{8.6} (6.9)\tnote{123} \\
    Attention/memory (0--36) & 2.8 (4.2)\tnote{24} & 8.9 (8.1)\tnote{134} & 3.2 (4.4)\tnote{24} &
    \textbf{15.6} (11.1)\tnote{123} \\
    Gastrointestinal (0--36) & 2.8 (3.9)\tnote{234} & 8.8 (7.1)\tnote{134} & 4.1
    (4.7)\tnote{124} & \textbf{14.6} (9.6)\tnote{123} \\
    Urinary (0--36) & 4.5 (5.9)\tnote{234} & 12.4 (9.7)\tnote{134} & 6.1 (6.4)\tnote{124} &
    \textbf{20.3} (9.9)\tnote{123} \\
    Sexual function (0--24) & 1.5 (3.1)\tnote{24} & 6.4 (7.4)\tnote{134} & 2.5 (4.1)\tnote{24} &
    \textbf{9.0} (9.7)\tnote{123} \\
    Miscellaneous (0--48) & 3.9 (4.7)\tnote{24} & 13.2 (8.6)\tnote{13} & 5.2 (5.8)\tnote{24} &
    \textbf{14.0} (9.5)\tnote{13} \\
    \midrule
    \textbf{Motor} & & & & \\
    Tremor & 1.9 (1.8)\tnote{34} & 1.6 (1.9)\tnote{34} & \textbf{4.3} (2.8)\tnote{124} & 3.5
    (3.8)\tnote{123} \\
    Bradykinesia & 1.5 (0.9)\tnote{234} & 2.1 (1.1)\tnote{134} & 3.6 (0.9)\tnote{124} &
    \textbf{4.0} (1.5)\tnote{123} \\
    Rigidity & 1.5 (0.9)\tnote{234} & 1.8 (1.1)\tnote{134} & 3.3 (0.9)\tnote{124} &
    \textbf{3.8} (1.4)\tnote{123} \\
    Axial & 1.8 (1.6)\tnote{234} & 3.3 (2.1)\tnote{134} & 4.3 (2.4)\tnote{124} &
    \textbf{7.4} (2.9)\tnote{123} \\
    \bottomrule
  \end{tabular}
  \begin{tablenotes}
    \small
    \item[1] Significant difference with cluster 1 ($p < 0.05$)
    \item[2] Significant difference with cluster 2 ($p < 0.05$)
    \item[3] Significant difference with cluster 3 ($p < 0.05$)
    \item[4] Significant difference with cluster 4 ($p < 0.05$)
    \item[\textdagger] Another footnote.
  \end{tablenotes}
  \end{threeparttable}
\end{table*}

@@

\begin{table*}[t]
  \centering
  \caption{Cluster statistics for variables not used in the analysis}
  \label{tab:nmd_extra}
  \begin{threeparttable}
  \begin{tabular}{l r r r r}
    \toprule
    & 1 & 2 & 3 & 4 \\
    \midrule
      Age & 62.7 (9.7) & 64 (9) & 65 (10.2) & 70.5 (8.9) \\
      Sex & 0.4 (0.5) & 0.5 (0.5) & 0.3 (0.5) & 0.4 (0.5) \\
      PD\_Onset & 56 (10.6) & 55.2 (10.1) & 56.9 (11.1) & 58.2 (11.4) \\
      PD\_Duration & 6.7 (4.8) & 8.7 (5.7) & 8 (5.5) & 12.3 (8.1) \\
      CISI\_Total & 5.7 (3.2) & 9.2 (3.9) & 9.7 (3.5) & 14.8 (5.1) \\
      Surgery & 0 (0.2) & 0.1 (0.2) & 0 (0.2) & 0 (0.1) \\
    \bottomrule
  \end{tabular}
  \begin{tablenotes}
    \small
    \item[1] Significant difference with cluster 1 ($p < 0.05$)
    \item[2] Significant difference with cluster 2 ($p < 0.05$)
    \item[3] Significant difference with cluster 3 ($p < 0.05$)
    \item[4] Significant difference with cluster 4 ($p < 0.05$)
    \item[\textdagger] Another footnote.
  \end{tablenotes}
  \end{threeparttable}
\end{table*}
\subsection{Clustering with nonmotor symptoms}

@@

$k$-means clustering on this Parkinsons' Disease data set reveals clusters that confirm previous
findings in the field, mainly van Rooden et al.\cite{vanrooden10} and the identification of four
subtypes of Parkinson's disease: mild, nonmotor-predominant, motor-predominant, and severe.  van
Rooden's work was done with a separate dataset using a different modeling method
(expectation-maximization), and this investigation independently confirms these subtype
classifications. Unlike van Rooden, mean disease durations differences do exist between subtypes 1
(mild) and 4 (severe), likely due to further development of the disease, although the differences
between 2 and 3 (nonmotor/motor predominated) subtypes are insignificant
(Table~\ref{tab:tukeyhsd}), suggesting different developmental paths of the disease.

@@

It remains to be seen whether these classification models, especially the one-vs-all decision
trees, are useful in clinical practice.

\subsection{New conclusions}
\label{ssec:newconc}

>>>>

% Use times font
\usepackage{mathptmx}
\usepackage{lmodern}

@@

% Tables, Figures
\usepackage{booktabs}
\usepackage{threeparttable}
% For line-breaking cells
\newcommand{\spc}[2][c]{%
  \begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
\usepackage{float}
\usepackage{caption}
\setlength{\tabcolsep}{10pt}

@@

Out of the 951 patients in the study, we used listwise deletion to exclude 47 patients due to
missing measurements in the variables of interest, resulting in 904 remaining patients. All
symptoms were scaled to $z$-scores ($\mu = 0$, $\sigma = 1$) before clustering, and unscaled
afterwards. Analysis was conducted in R 3.2.4 (www.r-project.org).

@@

For each symptom in both clusterings, we used one-way ANOVA and $\chi^2$ tests to test the equality
of symptom means and proportions across the clusters found, using Bonferroni correction for
multiple testing with corrected $p < 0.05$ considered significant. Differences among pairwise
clusters were tested post-hoc using Tukey's range test for continuous means, or pairwise $\chi^2$
tests with Bonferroni correction for proportions.

@@

$k$-means clustering on the nine nonmotor domains and the four motor symptoms found four clusters,
available in Table~\ref{tab:nmd} with boxplots in Figure~\ref{fig:box}. Cluster means for all
symptoms were found to be statistically different $(p < 0.05 / 13 \approx 0.003)$, with specific
pairwise differences noted in the table. Additionally, statistics for variables not used in the
clustering were explored similarly in Table~\ref{tab:nmd_extra}; cluster means for all variables
were found to be statistically different, except for PD onset.

Cluster 1 ($n = 406$) patients were mildly affected in all domains. This cluster was characterized
by relatively lower disease durations and ages.

Cluster 2 ($n = 189$) patients were severely affected in nonmotor domains but mildly affected in
motor domains. This cluster had an incidence of motor symptoms relatively similar to the Cluster 1
(mild) subtype especially in tremor, but generally expressed significantly higher scores for
nonmotor symptoms than Clusters 1 and 3, especially in the sleep/fatigue, mood/cognition and
miscellaneous domains.
% But also high variability

Cluster 3 ($n = 221$) patients were severely affected in motor domains but mildly affected in
nonmotor domains. Mean motor scores were greater than the means of clusters 1 and 2, but less than
4, with the exception of tremor, which was especially high.

Cluster 4 ($n = 88$) patients were severely affected in all domains, having the greatest symptom
mean out of all four clusters with the exception of tremor. Consequently, patients in Cluster 4 had
the longest average PD duration and oldest ages, but did not have a significantly different age of
PD onset.

\begin{table*}[t]
  \centering
  \caption{Summaries of clustering on nonmotor domains. Unless otherwise specified, statistics are
    reported as mean (sd). \textbf{Bold} indicates the highest score for that symptom out of the
  four clusters.}
  \label{tab:nmd}
  \begin{threeparttable}
  \begin{tabular}{l r r r r}
    \toprule
    Cluster & 1 & 2 & 3 & 4 \\
    $n$ & 406 (45\%) & 189 (21\%) & 221 (24\%) & 88 (10\%) \\
    \midrule
    \textbf{Nonmotor} (Domains) & & & & \\
    Cardiovascular (0--24) & 0.7 (1.6)\tnote{24} & 2.3 (2.9)\tnote{134} & 1.1 (2.0)\tnote{24} &
    \textbf{7.0} (6.0)\tnote{234} \\
    Sleep/fatigue (0--48) & 4.3 (4.8)\tnote{234} & 14.9 (8.2)\tnote{134} & 6.9 (6.3)\tnote{124}
    & \textbf{21.0} (10.0)\tnote{123} \\
    Mood/cognition (0--60) & 3.1 (4.5)\tnote{234} & 16.1 (14.0)\tnote{134} & 6.6
    (8.1)\tnote{124} & \textbf{23.4} (14.3)\tnote{123} \\
    Perception/hallucination (0--36) & 0.5 (1.7)\tnote{24} & 1.9 (3.5)\tnote{134} & 0.8
    (2.0)\tnote{24} & \textbf{8.6} (6.9)\tnote{123} \\
    Attention/memory (0--36) & 2.8 (4.2)\tnote{24} & 8.9 (8.1)\tnote{134} & 3.2 (4.4)\tnote{24} &
    \textbf{15.6} (11.1)\tnote{123} \\
    Gastrointestinal (0--36) & 2.8 (3.9)\tnote{234} & 8.8 (7.1)\tnote{134} & 4.1
    (4.7)\tnote{124} & \textbf{14.6} (9.6)\tnote{123} \\
    Urinary (0--36) & 4.5 (5.9)\tnote{234} & 12.4 (9.7)\tnote{134} & 6.1 (6.4)\tnote{124} &
    \textbf{20.3} (9.9)\tnote{123} \\
    Sexual function (0--24) & 1.5 (3.1)\tnote{24} & 6.4 (7.4)\tnote{134} & 2.5 (4.1)\tnote{24} &
    \textbf{9.0} (9.7)\tnote{123} \\
    Miscellaneous (0--48) & 3.9 (4.7)\tnote{24} & 13.2 (8.6)\tnote{13} & 5.2 (5.8)\tnote{24} &
    \textbf{14.0} (9.5)\tnote{13} \\
    \midrule
    \textbf{Motor} & & & & \\
    Tremor & 1.9 (1.8)\tnote{34} & 1.6 (1.9)\tnote{34} & \textbf{4.3} (2.8)\tnote{124} & 3.5
    (3.8)\tnote{123} \\
    Bradykinesia & 1.5 (0.9)\tnote{234} & 2.1 (1.1)\tnote{134} & 3.6 (0.9)\tnote{124} &
    \textbf{4.0} (1.5)\tnote{123} \\
    Rigidity & 1.5 (0.9)\tnote{234} & 1.8 (1.1)\tnote{134} & 3.3 (0.9)\tnote{124} &
    \textbf{3.8} (1.4)\tnote{123} \\
    Axial & 1.8 (1.6)\tnote{234} & 3.3 (2.1)\tnote{134} & 4.3 (2.4)\tnote{124} &
    \textbf{7.4} (2.9)\tnote{123} \\
    \bottomrule
  \end{tabular}
  \begin{tablenotes}
    \small
    \item[1] Significant difference with cluster 1 (adjusted $p < 0.05$)
    \item[2] Significant difference with cluster 2 (adjusted $p < 0.05$)
    \item[3] Significant difference with cluster 3 (adjusted $p < 0.05$)
    \item[4] Significant difference with cluster 4 (adjusted $p < 0.05$)
    \item[\textdagger] Another footnote.
  \end{tablenotes}
  \end{threeparttable}
\end{table*}

@@

\begin{table*}[t]
  \centering
  \caption{Cluster statistics for variables not used in the analysis}
  \label{tab:nmd_extra}
  \begin{threeparttable}
  \begin{tabular}{l r r r r}
    \toprule
    Cluster & 1 & 2 & 3 & 4 \\
    \midrule
      Sex (\% male) & 63 & 53\tnote{3} & 71\tnote{2} & 58 \\
      Age & 62.7 (9.7)\tnote{34} & 64 (9.0)\tnote{4} & 65 (10.2)\tnote{14} & 70.5 (8.9)\tnote{123} \\
      PD\_Onset & 56 (10.6) & 55.2 (10.1) & 56.9 (11.1) & 58.2 (11.4) \\
      PD\_Duration & 6.7 (4.8)\tnote{234} & 8.7 (5.7)\tnote{14} & 8 (5.5)\tnote{14} & 12.3
      (8.1)\tnote{123} \\
      CISI\_Total & 5.7 (3.2)\tnote{234} & 9.2 (3.9)\tnote{14} & 9.7 (3.5)\tnote{14} & 14.8
      (5.1)\tnote{123} \\
    \bottomrule
  \end{tabular}
  \begin{tablenotes}
    \small
    \item[1] Significant difference with cluster 1 (adjusted $p < 0.05$)
    \item[2] Significant difference with cluster 2 (adjusted $p < 0.05$)
    \item[3] Significant difference with cluster 3 (adjusted $p < 0.05$)
    \item[4] Significant difference with cluster 4 (adjusted $p < 0.05$)
  \end{tablenotes}
  \end{threeparttable}
\end{table*}

\subsection{Clustering with nonmotor symptoms}

$k$-means clustering performed on the 30 individual nonmotor symptoms found similar patterns to the
first clustering (Table~\ref{tab:nms30}, heatmap in Figure~\ref{fig:nms30-hm}). Means of all symptoms were found to
differ across clusters except for PD\_Onset and tremor.

Clusters 1 ($n = 509$) and 4 ($n = 49$), the mild and severe subtypes of the previous clustering,
retain their characteristics here, while clusters 2 ($n = 97$) and 3 ($n = 249$) are different. 2
is a mood/cognition-dominant cluster, with relatively higher proportion of female patients and
additionally a relatively more severe incidence of insomnia. 3 is not characterized by any
especially high symptoms and is thus an ``average'' group of patients.
% Once again, CISI TOTAL...

% Perhaps this table belongs in appendix?
\begin{table*}[t]
  \centering
  \caption{Summaries of clustering on individual nonmotor domains. Unless otherwise specified,
    statistics are reported as mean (sd). \textbf{Bold} indicates the highest score for that
  symptom out of the four clusters.}
  \label{tab:nms30}
  \begin{threeparttable}
  \small
\begin{tabular}{lrllll}
  \toprule
    & Cluster & 1 & 2 & 3 & 4 \\
    & $n$ & 509 (56.3\%) & 97 (10.7\%) & 249 (27.5\%) & 49 (5.4\%) \\
  \midrule
  1.\ Cardiovascular &
  Lightheadedness & 0.6 (1.3)\tnote{234} & 2.4 (3.0)\tnote{14} & 2.1 (2.9)\tnote{14} & \textbf{5.2}
  (4.2)\tnote{123} \\
  &Fainting & 0.1 (0.7)\tnote{24} & 0.5 (1.4)\tnote{134} & 0.2 (0.6)\tnote{24} & \textbf{2.4}
  (3.5)\tnote{123} \\
  \midrule
  2.\ Sleep/fatigue &
  Drowsiness & 1.0 (1.9)\tnote{234} & 2.8 (3.3)\tnote{14} & 2.5 (3.0)\tnote{14} & \textbf{7.0}
  (3.8)\tnote{123} \\
  &Fatigue & 1.3 (2.0)\tnote{234} & 6.3 (4.2)\tnote{13} & 4.8 (3.9)\tnote{124} & \textbf{7.3} (3.5)\tnote{13} \\
  &Insomnia & 1.2 (2.6)\tnote{234} & \textbf{5.5} (4.8)\tnote{13} & 3.2 (3.8)\tnote{12} & 4.2
  (3.9)\tnote{1} \\
  &RLS & 0.7 (1.6)\tnote{234} & 2.3 (3.5)\tnote{14} & 1.9 (3.2)\tnote{14} & \textbf{3.9}
  (3.9)\tnote{123} \\
  \midrule
  3.\ Mood/cognition &
  Loss\_interest & 0.4 (1.1)\tnote{234} & \textbf{6.1} (3.8)\tnote{134} & 1.0 (1.8)\tnote{124} & 4.6 (3.7)\tnote{123} \\
  &Loss\_activities & 0.7 (1.6)\tnote{234} & \textbf{7.1} (4.1)\tnote{134} & 1.7 (2.4)\tnote{124} &
  5.4 (4.0)\tnote{123} \\
  &Anxiety & 0.9 (1.8)\tnote{234} & \textbf{6.6} (4.3)\tnote{134} & 2.0 (2.8)\tnote{124} & 4.6 (3.9)\tnote{123} \\
  &Depression & 0.8 (1.6)\tnote{234} & \textbf{7.8} (3.7)\tnote{134} & 2.3 (3.0)\tnote{124} & 4.3 (3.7)\tnote{123} \\
  &Flat\_affect & 0.4 (1.1)\tnote{234} & \textbf{4.9} (4.3)\tnote{134} & 0.9 (1.9)\tnote{124} & 2.7 (3.0)\tnote{123} \\
  &Loss\_pleasure & 0.4 (1.2)\tnote{234} & \textbf{6.8} (4.1)\tnote{134} & 1.1 (2.1)\tnote{124} & 3.4 (3.3)\tnote{123} \\
  \midrule
  % This one is spread across multiple cells
  4.\ Perception/ & Hallucination & 0.2 (1.0)\tnote{234} & 0.8 (1.9)\tnote{14} & 0.6 (1.6)\tnote{14} & \textbf{4.6} (3.6)\tnote{123} \\
  hallucination &Delusion & 0.1 (0.7)\tnote{24} & 1.5 (3.1)\tnote{124} & 0.2 (1.0)\tnote{24} &
  \textbf{3.1} (3.8)\tnote{123} \\
  &Diplopia & 0.2 (0.7)\tnote{234} & 1.0 (2.5)\tnote{14} & 0.6 (1.4)\tnote{14} & \textbf{4.4}
  (4.3)\tnote{123} \\
  \midrule
  5.\ Attention/ & Loss\_concentration & 0.9 (1.8)\tnote{234} & 4.0 (3.6)\tnote{134} & 2.5 (3.1)\tnote{124} & \textbf{6.6} (3.9)\tnote{123} \\
  memory &Forget\_explicit & 0.9 (1.6)\tnote{234} & 3.8 (3.9)\tnote{134} & 2.2 (2.9)\tnote{124} & \textbf{6.7} (3.6)\tnote{123} \\
  &Forget\_implicit & 0.7 (1.6)\tnote{234} & 3.1 (3.7)\tnote{134} & 1.8 (2.6)\tnote{124} & \textbf{6.7} (4.0)\tnote{123} \\
  \midrule
  6.\ Gastrointestinal &
  Drooling & 0.7 (1.6)\tnote{234} & 3.0 (4.1)\tnote{14} & 3.0 (3.8)\tnote{14} & \textbf{6.1} (4.4)\tnote{123} \\
  &Swallowing & 0.4 (1.2)\tnote{234} & 1.2 (2.1)\tnote{14} & 1.7 (2.8)\tnote{14} & \textbf{4.5} (3.9)\tnote{123} \\
  &Constipation & 1.6 (2.9)\tnote{234} & 3.6 (4.3)\tnote{14} & 3.3 (4.1)\tnote{14} & \textbf{7.0} (5.1)\tnote{123} \\
  \midrule
  7.\ Urinary &
  Urinary\_urgency & 1.0 (1.8)\tnote{234} & 3.5 (4.1)\tnote{14} & 3.8 (3.8)\tnote{14} & \textbf{7.8} (4.0)\tnote{123} \\
  &Urinary\_frequency & 0.9 (1.9)\tnote{234} & 4.0 (4.1)\tnote{14} & 3.8 (4.0)\tnote{14} & \textbf{6.5} (4.0)\tnote{123} \\
  &Nocturia & 1.7 (2.3)\tnote{234} & 5.0 (4.3)\tnote{14} & 5.1 (4.1)\tnote{14} & \textbf{7.7} (3.9)\tnote{123} \\
  \midrule
  8.\ Sexual &
  Sex\_drive & 0.8 (1.9)\tnote{234} & 4.5 (4.9)\tnote{13} & 2.3 (3.6)\tnote{124} & \textbf{5.2} (5.4)\tnote{13} \\
  &Sex\_dysfunction & 0.8 (2.2)\tnote{234} & 3.2 (4.7)\tnote{1} & 2.4 (3.8)\tnote{14} &
  \textbf{4.6} (5.4)\tnote{13} \\
  \midrule
  9.\ Miscellaneous &
  Unexplained\_pain & 0.7 (1.9)\tnote{234} & 2.5 (3.7)\tnote{14} & 3.0 (4.1)\tnote{14} & \textbf{4.2} (4.3)\tnote{123} \\
  &Gustation\_olfaction & 1.5 (2.9)\tnote{234} & 3.6 (4.3)\tnote{1} & 3.2 (3.9)\tnote{14} &
  \textbf{4.7} (4.8)\tnote{13} \\
  &Weight\_change & 0.9 (1.7)\tnote{234} & 2.5 (3.4)\tnote{14} & 1.9 (3.0)\tnote{14} & \textbf{3.9} (4.2)\tnote{123} \\
  &Sweating & 0.7 (1.8)\tnote{234} & 2.2 (3.5)\tnote{1} & 2.8 (4.1)\tnote{1} & \textbf{3.2}
  (3.8)\tnote{1} \\
  \midrule
  Motor &
  Tremor & 2.5 (2.3) & 2.1 (2.4) & 2.6 (2.6) & \textbf{4.1} (4.3) \\
  &Bradykinesia & 2.0 (1.2)\tnote{234} & 2.8 (1.4)\tnote{14} & 2.8 (1.4)\tnote{14} & \textbf{3.9} (1.8)\tnote{123} \\
  &Rigidity & 1.9 (1.2)\tnote{234} & 2.4 (1.3)\tnote{14} & 2.6 (1.4)\tnote{14} & \textbf{3.6} (1.6)\tnote{123} \\
  &Axial & 2.2 (1.8)\tnote{234} & 4.4 (2.8)\tnote{14} & 4.2 (2.7)\tnote{14} & \textbf{7.2} (3.2)\tnote{123} \\
  \midrule
  Variables not & Age & 62.7 (9.9)\tnote{34} & 64.5 (9.6)\tnote{4} & 66 (9.2)\tnote{14} & 71.5
  (8.1)\tnote{123} \\
  used in analysis & Sex (\% Male) & 65\tnote{2} & 51\tnote{1} & 60 & 63 \\
  & PD\_Onset & 55.9 (10.8) & 56.2 (10.4) & 56.7 (10.5) & 57.8 (11.0) \\
  & PD\_Duration & 6.8 (4.8)\tnote{34} & 8.3 (5.3)\tnote{4} & 9.3 (6.3)\tnote{14} & 13.8
  (8.2)\tnote{123} \\
  & CISI\_Total & 6.3 (3.4)\tnote{234} & 10.8 (4.7)\tnote{14} & 10 (4.0)\tnote{14} & 15.1 (5.7)\tnote{123} \\
   \bottomrule
\end{tabular}
  \begin{tablenotes}
    \small
    \item[1] Significant difference with cluster 1 (adjusted $p < 0.05$)
    \item[2] Significant difference with cluster 2 (adjusted $p < 0.05$)
    \item[3] Significant difference with cluster 3 (adjusted $p < 0.05$)
    \item[4] Significant difference with cluster 4 (adjusted $p < 0.05$)
  \end{tablenotes}
  \end{threeparttable}
\end{table*}

% TODO: If the outline of the paper is good enough it might be possible to have this inline
% in the paper somewhere. If so, change figure* -> figure, make h! (force horizontal?), and switch
% 0.8 linewidth to full linewidth
% Also, I'm going to include this AFTER nms30m-colhc, so that colhc/boxplots fits nicely on one
% page
\begin{figure*}[p]
  \centering
  \includegraphics[width=0.7\linewidth]{nms30-hm-pub.pdf}
  % TODO: Variables not used in analysis? Label color - black nms, blue nonmotor, grey ?
  \caption{Heatmap of clusters found when clustering with nonmotor symptoms. Color indicates
    cluster mean as a $z$-score for the given symptom; red is higher, green is lower.}
  \label{fig:nms30-hm}
\end{figure*}

@@

$k$-means clustering on this dataset reveals clusters that confirm previous
findings in the field, mainly van Rooden et al.\cite{vanrooden10} and the identification of four
subtypes of Parkinson's disease: mild, nonmotor-predominant, motor-predominant, and severe.  van
Rooden's work was done with a separate dataset using a different modeling method
(expectation-maximization), and this investigation independently confirms these subtype
classifications. Unlike van Rooden, mean disease durations differences do exist between subtypes 1
(mild) and 4 (severe), likely due to further development of the disease, although the differences
between 2 and 3 (nonmotor/motor predominated) subtypes are insignificant
(Table~\ref{tab:tukeyhsd}), suggesting different developmental paths of the disease.

@@
